Whats reported in the news?

### 2018-04-05 paper/docs/04_Modelresults_50.Rmd
add tables

coeff <- coeff %>% 
  mutate(parameter = rownames(coeff),
         parameter = gsub("site", "", parameter),
         signifcant = ifelse(p <= 0.5,"yes","no")) %>%
  left_join(., topics.df, by="topic")
```

@@

```{r fig.height=4, fig.width=10}
p1 <- coeff %>% 
  filter(topic %in% keep) %>%
  filter(parameter %in% stmOut$settings$covariates$yvarlevels) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col(alpha = 0.8) +
  scale_fill_manual(values = col[c(5,3)]) +
  scale_x_discrete(position = "top") +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))

ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 9, height = 6,
dpi = 600)
```

>>>>

coeff <- coeff %>% 
  mutate(parameter = rownames(coeff),
         parameter = gsub("site", "", parameter),
         signifcant = ifelse(p <= 0.5,"yes","no")) %>%
  left_join(., topics.df, by="topic") %>%
  mutate(parameter = ifelse(parameter == "welt.de", "DIE WELT", parameter),
         parameter = ifelse(parameter == "zeit.de", "ZEIT ONLINE", parameter),
         parameter = ifelse(parameter == "focus.de", "FOCUS ONLINE", parameter),
         parameter = ifelse(parameter == "spiegel.de", "SPIEGEL ONLINE", parameter),
         parameter = ifelse(parameter == "tagesschau.de", "Tagesschau.de", parameter))
```

```{r}
nr <- nrow(coeff)/5

coeff_tab <- coeff %>%
  select(topic_name,parameter,Estimate, `Std. Error`, `t value`, p)

print(xtable(coeff_tab[1:nr,], type="latex"), file="../writing/tables/coeff1.tex" )
print(xtable(coeff_tab[nr:(nr*2),], type="latex"), file="../writing/tables/coeff2.tex" )
print(xtable(coeff_tab[(nr*2):(nr*3),], type="latex"), file="../writing/tables/coeff3.tex" )
print(xtable(coeff_tab[(nr*3):(nr*4),], type="latex"), file="../writing/tables/coeff4.tex" )
print(xtable(coeff_tab[(nr*4):(nr*5),], type="latex"), file="../writing/tables/coeff5.tex" )
```

@@

```{r fig.height=4, fig.width=10}
p1 <- coeff %>% 
  filter(topic %in% keep) %>%
  filter(parameter != "(Intercept)") %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col(alpha = 0.8) +
  scale_fill_manual(values = col[c(5,3)]) +
  scale_x_discrete(position = "top") +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))
ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 9, height = 6,
dpi = 600)
```
